---
title: "Assignment V"
author: "Roßkopf Steffen"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, message=FALSE, include=FALSE}

rm(list = ls())

if(!require("httr")) install.packages("httr")
if(!require("tidyverse")) install.packages("tidyverse")
if(!require("jsonlite")) install.packages("jsonlite")
if(!require("rlist")) install.packages("rlist")
if(!require("magrittr")) install.packages("magrittr")
if(!require("janitor")) install.packages("janitor")

library(httr)
library(tidyverse)
library(jsonlite)
library(rlist)
library(magrittr)
library(janitor)
```


# 1. Setting up a new GitHub repository
• Register on github.com in case you have not done this already.

• Initialize a new public repository for this assignment on GitHub.

• For the following exercises of this assignment, follow the standard Git workflow (i.e., pull the latest
version of the project to your local computer, then stage, commit, and push all the modifications that
you make throughout the project). Every logical programming step should be well documented on
GitHub with a meaningful commit message, so that other people (e.g., your course instructor) can
follow understand the development history. You can to do this either using Shell commands or a Git
GUI of your choice.

• In the HTML file that you submit, include the hyperlink to the project repository

-> [here](https://github.com/rosskost/assignment_V) is the link to my repository

# 2. Getting to know the API
• Visit the documentation website for the API provided by ticketmaster.com (see [here](https://developer.ticketmaster.com/products-and-docs/apis/getting-started/)).

• Familiarize yourself with the features and functionalities of the Ticketmaster Discovery API. Have a
particular look at rate limits.

• Whithin the scope of this assignment, you do not have to request your own API key. Instead retrieve
a valid key from the API Explorer. This API key enables you to perform the GET requests needed
throughout this assignment.

• Even though this API key is not secret per se (it is publicly visible onn the API Explorer website),
please comply to the common secrecy practices discussed in the lecture and the tutorial: Treat the API
key as a secret token. Your API key should neither appear in the code that you are submitting nor in
your public GitHub repository.

```{r}
source("./key.R")
# users of this file, get your own api-key at:
# https://developer.ticketmaster.com/api-explorer/v2/
  
```

# 3. Interacting with the API - the basics
• Load the packages needed to interact with APIs using R.

• Perform a first GET request, that searches for event venues in Germany (countryCode = "DE"). Extract
the content from the response object and inspect the resulting list. Describe what you can see.

```{r}

response_events_ger <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues",
                           query = list(apikey = api_key,
                                        countryCode = 'DE',
                                        locale = '*',
                                        page = 0))

status_code(response_events_ger)  # succesful
    
content_events_ger <- fromJSON(content(response_events_ger, as = "text")) # put json-content in R list



# the response list 'content_events_ger' consists of three main-lists. '_embedded', '_links' and 'page'.
# in _embedded.venues we find the relevant data we are looking for. Some of them are again a list. We recieved 20 observations.
# in _links we can find information on our search, on page information on which page we are and how many
# more observations we can get.


```


• Extract the name, the city, the postalCode and address, as well as the url and the longitude and
latitude of the venues to a data frame. This data frame should have the following structure:
glimpse(venue_data)

```{r}
df_venues <- as.data.frame(list.flatten(content_events_ger)) %>% 
  select(contains(
    c('venues.name','city.name','postalCode','address','venues.url','longitude','latitude'))) %>%              set_colnames(c('name','city','postal_code','address','url','longitude','latitude')) %>% 
  mutate("longitude" = as.numeric(longitude),
         "latitude" = as.numeric(latitude))

glimpse(df_venues)

```


# 4. Interacting with the API - advanced
• Have a closer look at the list element named page. Did your GET request from exercise 3 return all
event locations in Germany? Obviously not - there are of course much more venues in Germany than
those contained in this list. Your GET request only yielded the first results page containing the first 20
out of several thousands of venues.

• Check the API documentation under the section Venue Search. How can you request the venues from
the remaining results pages?

```{r}
# there is a page-argument, which we can hand over
```


• Write a for loop that iterates through the results pages and performs a GET request for all venues
in Germany. After each iteration, extract the seven variables name, city, postalCode, address, url,
longitude, and latitude. Join the information in one large data frame.
```{r}

get_venues_of_country_ticketmaster <- function (country_code = "DE", api_key) {
  
  # idea: we make one get-request to get the number of elements and pages were looking for,
  # after that we use a loop to get all elements.
  
  initial_response <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues",
                           query = list(apikey = api_key,
                                        countryCode = country_code,
                                        locale = '*',
                                        page = 0))
  initial_content_parsed <- fromJSON(content(initial_response, as = "text", encoding = "UTF-8"))
  
  dimensions_search <- unlist(initial_content_parsed[["page"]]) # get dimensions of our search
  
  size_page <- dimensions_search[1]
  n <- dimensions_search[2]   # number of observations/row in whole response
  number_pages <- dimensions_search[3]
  
  # df we store data in:
  df_venues_country <- data.frame(  
    name = character(n),
    city = character(n),
    postal_code = character(n),
    adress = character(n),
    url = character(n),
    longitude = integer(n),
    latitude = integer(n),
    stringsAsFactors = FALSE
  )

  Sys.sleep(0.2)
  
  for (page in 0:18) {
    if (page == number_pages) {  # if we are on the last page, size ==?
         response <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues",
                           query = list(apikey = api_key,
                                        countryCode = country_code,
                                        locale = '*',
                                        page = as.character(page),
                                        size = n %% size_page)) # at last page only receive last few rows
         
         content_parsed <- fromJSON(
           content(response, as = "text", encoding = "UTF-8"), flatten = TRUE)[["_embedded"]][["venues"]]
         
         df_venues_country[(page * size_page - n %% size_page):(n), ] <- content_parsed %>%
           select(name, city.name, postalCode, address.line1, url, location.longitude, location.latitude)
      
    } else {
       response <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues",
                           query = list(apikey = api_key,
                                        countryCode = country_code,
                                        locale = '*',
                                        page = as.character(page)))
       content_parsed <- fromJSON(
         content(response, as = "text", encoding = "UTF-8"), flatten = TRUE)[["_embedded"]][["venues"]]
       df_venues_country[(page * size_page + 1):((page+1)* size_page), ] <- content_parsed %>%
         select(name, city.name, postalCode, address.line1, url, location.longitude, location.latitude)
       
       Sys.sleep(0.2) # documentation api,  at max 5 request per second.
    }
  }
  
  return(df_venues_country)
}

```


```{r}
df_venues_full = get_venues_of_country_ticketmaster(country_code = "AT", api_key)

```
 

• The resulting data frame should look something like this (note that the exact number of search results
may have changed since this document has been last modified):
```{r}

response_de <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues",
                           query = list(apikey = api_key,
                                        countryCode = "DE",
                                        locale = '*',
                                        page = 0))

status_code(response_de)
  

content_parsed_de <- fromJSON(content(response_de, as = "text", encoding = "UTF-8"))

dimensions_search <- unlist(content_parsed_de[["page"]])
dimensions_search
    
content_parsed_at[["_embedded"]][["venues"]][["name"]]

n <- 12238

  df_venues_country <- data.frame(  
    name = character(n),
    city = character(n),
    postal_code = character(n),
    adress = character(n),
    url = character(n),
    longitude = integer(n),
    latitude = integer(n),
    stringsAsFactors = FALSE
  )


  response <- GET(url = "https://app.ticketmaster.com/discovery/v2/venues",
                           query = list(apikey = api_key,
                                        countryCode = 'DE',
                                        locale = '*',
                                        size = n))
       content_parsed <- fromJSON(
         content(response, as = "text", encoding = "UTF-8"), flatten = TRUE)[["_embedded"]][["venues"]]
       
       df_venues_country[1:n, ] <- content_parsed %>%
         select(name, city.name, postalCode, address.line1, url, location.longitude, location.latitude)


```
 
# 5. Visualizing the extracted data
• Below, you can find code that produces a map of Germany. Add points to the map indicating the
locations of the event venues across Germany.

• You will find that some coordinates lie way beyond the German borders and can be assumed to be faulty.
Set coordinate values to NA where the value of longitude is outside the range (5.866944, 15.043611)
or where the value of latitude is outside the range (47.271679, 55.0846) (these coordinate ranges
have been derived from the extreme points of Germany as listed on Wikipedia (see here). For extreme
points of other countries, see here).

```{r}
ggplot() +
geom_polygon(
aes(x = long, y = lat, group = group), data = map_data("world", region = "Germany"),
fill = "grey90",color = "black") +
theme_void() + coord_quickmap() +
labs(title = "Event locations across Germany", caption = "Source: ticketmaster.com") +
theme(title = element_text(size=8, face='bold'),
plot.caption = element_text(face = "italic"))

```



# 6. Event locations in other countries

• Repeat exercises 2 to 5 for another European country of your choice. (Hint: Clean code pays off! If you
have coded the exercises efficiently, only very few adaptions need to be made.)
















```{r fig.width=6, fig.height=6, fig.align='center', include=FALSE}


```

```{r, echo=FALSE, results='asis', include=FALSE}

knitr::kable(head(iris, 10))
```



